### 2015-09-17 tex/definitions.tex
Added defeq macro for definitions. Updated VS and ST function definitions, as well as summarize-precise figures. Changed bibliography style to get it to compile.

\section{Definitions}
\label{sec:defs}
\begin{definition}
The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
 $$\mathcal{R} = \mathbb{N}$$
\end{definition}

@@

\begin{definition}
The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
 $$\mathcal{R}_t =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$. 
\end{definition}

@@

\begin{definition}
The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
 $$\mathcal{R}_h =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$. 
\end{definition}

\begin{definition}
The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
 $$\mathcal{R}_f =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
\end{definition}

\begin{definition}
For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
\begin{align}
 f^\rightarrow &= \{ f(a) \mid a \in A\}\\
 f^\leftarrow &= \{ a \mid f(a) \in B \}
 \end{align}
 The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
 \begin{align}
 f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
 f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
 \end{align}
 Where $C \subset A$ and $D \subset B$
\end{definition}

@@

\begin{definition}
\label{def:state}
The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \ref{fig:machine-syntax}.
\end{definition}

@@

\begin{definition}
The universe of reachable states is $S$. The universe is further partitioned into states that activate different relations.
\begin{itemize}
\item Field Access, $S_\mathit{FA} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}\ (\cfgnt{e} = \cfgnt{r}) \wedge \exists \cfgnt{f},\cfgnt{k}_0\ (\cfgnt{k} = \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}_0\rp) \}$
\item Field Write,  $S_\mathit{FW} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}\ (\cfgnt{e} = \cfgnt{r}) \wedge \exists \cfgnt{x},\cfgnt{f},\cfgnt{k}_0\ (\cfgnt{k} = \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}_0\rp) \}$
\item Equals, $S_\mathit{EQ} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}_0 (\cfgnt{e} = \cfgnt{r}_0) \wedge \exists r_1, k_1(\cfgnt{k} = \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}_1\rp \}$
\item New, $S_\mathit{N} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{C}\ (\cfgnt{e} = \lp \cfgt{new}\ \cfgnt{C}\rp) \}$
\end{itemize} 
\end{definition}

\begin{definition}
Given a sequence of states $$\Pi_n = s_0,s_1,...,s_n$$ where $$s_i = (\cfgnt{L}_i\ \cfgnt{R}_i\ \phi_i\ \eta_i\ \cfgnt{e}_i\ \cfgnt{k}_i )$$ the \textbf{control flow sequence} of $\Pi_n$ is the defined as the sequence of tuples $$ \pi_n = \mathbb{CF}(\Pi_n) = (\eta_0\ \cfgnt{e}_0\ \cfgnt{k}_0),(\eta_1\ \cfgnt{e}_1\ \cfgnt{k}_1),...,(\eta_n\ \cfgnt{e}_n\ \cfgnt{k}_n)$$
\end{definition}

@@

\begin{definition}
\label{def:homomorphism}
A \textbf{homomorphism} $s_p \rightharpoonup_{h} s_q$, from state $s_p = ( \cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$ to state $s_q = ( \cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta_q\ \cfgnt{e}_q\ \cfgnt{k}_q )$, is defined as follows: 
$$
\begin{array}{l}
 s_p \rightharpoonup_{h} s_q \Leftrightarrow \\
\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}( \exists \phi_\alpha\ (\exists \phi_\beta\ ( \\ 
\ \ \ \ \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) ) ) )
\end{array}
$$
\begin{comment}
$$
\begin{array}{l}
s_p \rightharpoonup_{h} s_q \Leftrightarrow \\
\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathit{fields}(\mathrm{type}(\cfgnt{l}_\beta))\ ( \\
\ \ \ \ \ \ \ \ \ \ \ \ \forall (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f ))\ ( \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \exists \phi_\beta\ ((\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f )))))))\\
\end{array}
$$
\end{comment}
\end{definition}

@@

\begin{definition}
\label{def:hc}
Given the homomorphism $s_p \rightharpoonup_{h} s_q$, the \textbf{homomorphism constraint} $\mathbb{HC}(s_p \rightharpoonup_{h} s_q)$ is defined as:
\begin{align*}
\mathbb{HC}(s_p \rightharpoonup_{h} s_q) &= \\
 \bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\} 
\end{align*}
Where $\cfgnt{L}_p$ and $\cfgnt{L}_q$ are the locations maps from the heaps in $s_p$ and $s_q$.
\end{definition}

@@

\begin{definition}
\label{representation}
The \textbf{representation relation} $\sqsubset$ is defined as
follows: given state $s_p = (
\cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$
and state $s_q = (
\cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta_q\ \cfgnt{e}_q\ \cfgnt{k}_q )$,
$s_p \sqsubset s_q $ if and only if $\eta_p = \eta_q ,\ \cfgnt{e}_p =
\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, the heaps are well-formed, and there exists a
homomorphism $(\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h}
(\cfgnt{L}_q\ \cfgnt{R}_q)$ such that
\begin{equation}
\label{eqn:valid}
 \mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) ) 
\end{equation}
The represented relation is extended to sets of states $P$ and $Q$ as
$$
P \sqsubset Q \Longleftrightarrow \forall q \in Q\ (\forall p\ (p \sqsubset q \Rightarrow p \in P))
$$
\end{definition}

@@

\begin{definition}
\label{def:meta}
A state relation $p \rightarrow_x p^\prime$ is extended to sets of states $P \hookrightarrow_x P^\prime$ as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
The $\rgse$ relation over sets of states is $\rsgse = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FA(N)} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{FW(N)} \cup \hookrightarrow_\mathit{EQ(T)} \cup \hookrightarrow_\mathit{EQ(F)} \cup \hookrightarrow_\com$.%, and 
%the $\rsym$ relation extended to sets of states is 
%$$
%\rssym = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{EQ}^T \cup \hookrightarrow_\mathit{EQ}^F \cup \hookrightarrow_\com
%$$
\end{definition}

>>>>

\section{Definitions}
\label{sec:defs}
\begin{definition}
The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
 $$\mathcal{R} \defeq{} \mathbb{N}$$
\end{definition}

@@

\begin{definition}
The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
 $$\mathcal{R}_t \defeq{}\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$
\end{definition}

@@

\begin{definition}
The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
 $$\mathcal{R}_h \defeq{}\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$
\end{definition}

\begin{definition}
The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
 $$\mathcal{R}_f \defeq{}\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$ 
\end{definition}

\begin{definition}
For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
\begin{align}
 f^\rightarrow &\defeq{} \{ f(a) \mid a \in A\}\\
 f^\leftarrow &\defeq{} \{ a \mid f(a) \in B \}
 \end{align}
 The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
 \begin{align}
 f^\rightarrow [C] &\defeq{} \{ f(a) \mid a \in C\}\\
 f^\leftarrow [D] &\defeq{} \{ a \mid f(a) \in D \}
 \end{align}
 Where $C \subset A$ and $D \subset B$
\end{definition}

@@

\begin{definition}
\label{def:state}
The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \figref{fig:syntax}(b).
\end{definition}

@@

\begin{definition}
The universe of reachable states is $S$. The universe is further partitioned into states that activate different relations.
\begin{itemize}
\item Field Access, $S_\mathit{FA} \defeq{} \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}\ (\cfgnt{e} = \cfgnt{r}) \wedge \exists \cfgnt{f},\cfgnt{k}_0\ (\cfgnt{k} = \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}_0\rp) \}$
\item Field Write,  $S_\mathit{FW} \defeq{} \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}\ (\cfgnt{e} = \cfgnt{r}) \wedge \exists \cfgnt{x},\cfgnt{f},\cfgnt{k}_0\ (\cfgnt{k} = \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}_0\rp) \}$
\item Equals, $S_\mathit{EQ} \defeq{} \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}_0 (\cfgnt{e} = \cfgnt{r}_0) \wedge \exists r_1, k_1(\cfgnt{k} = \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}_1\rp \}$
\item New, $S_\mathit{N} \defeq{} \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{C}\ (\cfgnt{e} = \lp \cfgt{new}\ \cfgnt{C}\rp) \}$
\end{itemize} 
\end{definition}

\begin{definition}
Given a sequence of states $$\Pi_n = s_0,s_1,...,s_n$$ where $$s_i = (\cfgnt{L}_i\ \cfgnt{R}_i\ \phi_i\ \eta_i\ \cfgnt{e}_i\ \cfgnt{k}_i )$$ the \textbf{control flow sequence} of $\Pi_n$ is the defined as the sequence of tuples $$ \mathbb{CF}(\Pi_n) \defeq{} (\eta_0\ \cfgnt{e}_0\ \cfgnt{k}_0),(\eta_1\ \cfgnt{e}_1\ \cfgnt{k}_1),...,(\eta_n\ \cfgnt{e}_n\ \cfgnt{k}_n)$$
\end{definition}

@@

\begin{definition}
\label{def:homomorphism}
A \textbf{homomorphism}, given the universe of field indices $\mathcal{F}$ and the universe of locations $\mathcal{L}$, is 
$$
\begin{array}{l}
 s_p \rightharpoonup_{h} s_q\ \defeq \ 
\exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}\ ( \forall \phi_\alpha\ (\\ 
\ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow \\
\ \ \ \ \ \ \ \ \exists \phi_\beta\ ( (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ 
 )) ) ) ) )
\end{array}
$$
\end{definition}

@@

\begin{definition}
\label{def:hc}
The \textbf{homomorphism constraint} is
%\begin{align*}
\[
\mathbb{HC}(p \rightharpoonup_{h} q) \defeq
\bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\}
\]
%\end{align*}
\end{definition}

@@

\begin{definition}
\label{representation}
States $(p\ q)$ are in the \textbf{representation relation}, $p \sqsubset q$, if and only if, $\eta_p = \eta_q ,\ \cfgnt{e}_p =
\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a
homomorphism $p \rightharpoonup_{h} q$
such that $\mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) )$.
The represented relation is extended to sets of states $P$ and a single state $q$ as
$P \sqsubset q \defeq \forall p\ (p \sqsubset q \Leftrightarrow p \in P)$.
\end{definition}

@@

\begin{definition}
\label{def:meta}
Any state relation, say $\rightarrow_x^Y$, is extended to sets of states as
$$
P \hookrightarrow_x^Y P^\prime \defeq \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x^Y p^\prime \Leftrightarrow p^\prime \in P^\prime))
$$
The $\rgse$ relation over sets of states is $\rsgse = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FA(N)} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{FW(N)} \cup \hookrightarrow_\mathit{EQ(T)} \cup \hookrightarrow_\mathit{EQ(F)} \cup \hookrightarrow_\com$.%, and 
%the $\rsym$ relation extended to sets of states is 
%$$
%\rssym = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{EQ}^T \cup \hookrightarrow_\mathit{EQ}^F \cup \hookrightarrow_\com
%$$
\end{definition}

### 2015-09-17 tex/evaluation.tex
Added defeq macro for definitions. Updated VS and ST function definitions, as well as summarize-precise figures. Changed bibliography style to get it to compile.

%\subsection{Analysis}
The \symtxt{} algorithm is implemented as an extension to the Symbolic
PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13}
framework. In addition to the operations presented in this paper, the
implementation contains support for operations over integers,
calculating per-path preconditions and postconditions, as well as
generating test input heaps that exercise all feasible control flow
paths. Future work is adding support for floating point
operations, arrays, and bit-operations.

The \symtxt{} implementation uses \texttt{jConstraints} with the z3 solver \cite{ase2014-ghilrr,jpf2014-dghirr,deMouraBjorner08Z3}. The implementation takes advantage of incremental solving and employs caching for performance since only small portions of the heap constraint changes during the search.

>>>>

%\subsection{Analysis}
The~\symtxt{} algorithm is implemented as an extension to the Symbolic
PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13}
framework. In addition to the operations presented in this paper, the
implementation contains support for operations over integers,
calculating per-path preconditions and postconditions, as well as
generating test input heaps that exercise all feasible control flow
paths. Future work is adding support for floating point
operations, arrays, and bit-operations.

The~\symtxt{} implementation uses the z3 solver with ~\texttt{jConstraints}~\cite{ase2014-ghilrr,jpf2014-dghirr,deMouraBjorner08Z3}. The implementation takes advantage of incremental solving and employs caching for performance since only small portions of the heap constraint changes during the search.
